---
title: "Visualization with ggplot2"
author: "Eric Morris"
date: "9/27/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggridges)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

## Important NOAA Data 

```{r data_import, cache = TRUE}
library(rnoaa)

weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## Making a plot

Blank plot..

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))
```

Scatterplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

Filtering Central Park without having to also create a new data frame

```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

## More plot options

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```

Add a geom (se = FALSE will turn off confidence bands)

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name)) + 
  geom_smooth(se = FALSE)
```

Making points more transparent

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = 0.4) + 
  geom_smooth(se = FALSE)
```

Adding some more options and switching everything around

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.4) + 
  geom_smooth(se = FALSE)
```

Facetting...

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.4) + 
  geom_smooth(se = FALSE) +
  facet_grid( ~ name)
```

A more interesting plot 

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point()
```

Lines instead of points

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_line()
```

Back to points and adding more stuff

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name, size = prcp)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

## Univariate Plots

Histogram

```{r}
ggplot(weather_df, aes(x = tmax)) + 
  geom_histogram()
```

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_histogram()
```

Density mapping

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_density(alpha = 0.5)
```

Boxplots

```{r}
ggplot(weather_df, aes(x = name, y = tmax)) + 
  geom_boxplot()
```

Violin plot?

```{r}
ggplot(weather_df, aes(x = name, y = tmax)) + 
  geom_violin()
```

ggridges, flipping violins 

```{r}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges()
```

Saving plots -> adding little knitr snippet at beginning of markdown to make all graphs the same consistent size as well as increasing font size for when you save plots

```{r}
weather_plot = ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) 

ggsave("weather_plot.pdf", weather_plot, width = 8, height = 5)
```

## Last example

```{r}
ggplot(weather_df, aes(y = prcp, x = name)) +
  geom_boxplot()
```

```{r}
weather_df %>% 
  filter(prcp > 0) %>% 
  ggplot(aes(x = prcp, fill = name)) +
  geom_density(alpha = .5)
```

